---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# STDataMGMT

<!-- badges: start -->
<!-- badges: end -->

The goal of STDataMGMT is to generate private data for the stress test.

## Installation

You can install the development version of STDataMGMT from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Theia-Finance-Labs/STDataMGMT")
```

## Example

```{r example}
library(STDataMGMT)
library(tibble)

# Some of the included dataset
production_types

scenarios_geographies

synthetic_eikon_data
```

## Funding

The repository forms part of the LIFE STRESS project. The LIFE STRESS project
has received funding from the LIFE Programme of the European Union. The contents
of this publication are the sole responsibility of Theia Finance Labs and do not
necessarily reflect the opinion of the European Union. Project: 101074271 —
LIFE21-GIC-DE-Stress.

EU LIFE Project Grant

Co-funded by the European Union. Views and opinions expressed are however those
of the author(s) only and do not necessarily reflect those of the European Union
or CINEA. Neither the European Union nor the granting authority can be held
responsible for them.

Scientific Transition Risk Exercises for Stress tests & Scenario Analysis has
received funding from the European Union’s Life programme under Grant No.
LIFE21-GIC-DE-Stress under the LIFE-2021-SAP-CLIMA funding call.

<img src=data-raw/LifeLogo2.jpg width=150>

