---
title: "sample_abcd_input"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sample_abcd_input}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(STDataMGMT)
library(dplyr)
library(ggplot2)
library(tidyr)
```


# Functions


```{r}

count_n_companies <- function(abcd_data, group_cols=NULL){
  abcd_data |>
  distinct_at(c("company_id", group_cols)) |>
  group_by_at(group_cols) |>
  summarise(n_companies = dplyr::n(), .groups="drop")
}

sum_company_prod_volume <- function(abcd_data,group_cols=NULL){
  abcd_data |>
    group_by_at(c("company_id", group_cols)) |>
    summarise(plan_tech_prod=sum(plan_tech_prod), .groups="drop")
}

sum_total_prod_volume <- function(abcd_data, group_cols=NULL){
  abcd_data|>
  group_by_at(group_cols) |>
  summarise(plan_tech_prod=sum(plan_tech_prod), .groups="drop")
}

sum_yearly_prod_volume <- function(abcd_data, group_cols=NULL){
  abcd_data |>
  group_by_at(c("year", group_cols)) |>
  summarise(plan_tech_prod=sum(plan_tech_prod), .groups="drop")
}


add_company_diversity_col <- function(abcd_data){
    companies_diversity <- abcd_data |>
    distinct(company_id, ald_sector, ald_business_unit) |>
    group_by(company_id) |>
    summarise(n_bu = n())
    
    abcd_data |> inner_join(companies_diversity)
}

  # Function to calculate RMSE between two curves
  calculate_rmse <- function(curve1, curve2, group_cols=NULL) {
    # Assuming curve1 and curve2 are data frames with columns 'year' and 'plan_tech_prod'
    # Merge the two dataframes on 'year'
    merged_curves <- merge(curve1, curve2, by = c("year", group_cols))
    
    # Calculate the RMSE
    merged_curves <- merged_curves |>
      group_by_at(group_cols) |>
      summarise(rmse_group = sqrt(mean((
        .data$plan_tech_prod.x - .data$plan_tech_prod.y
      ) ^ 2
      )), .groups="drop")
    
    # Averages the RMSE
    rmse <-mean(merged_curves$rmse_group)
    
    return(rmse)
  }
  
  # Function for greedy search to sample companies
  sample_companies_greedy <-
    function(abcd_data,
             uniform_ratio,
             group_cols=NULL,
             n_sampling_attempts = 5,
             greedy_lr = 0.02,
             use_weighting=TRUE) {
      
      full_prod_volume_per_group <- sum_total_prod_volume(abcd_data, group_cols=group_cols)
      yearly_full_prod_volume_per_group <-sum_yearly_prod_volume(abcd_data, group_cols=group_cols)
      
      best_sample <- NULL
      best_ratio_diff <- Inf
      best_rmse <- Inf
      greedy_sampling_ratio <- 1
      
      # cat(abcd_data |> distinct(ald_sector, ald_business_unit))
      
      if (use_weighting){
        abcd_data <- add_company_diversity_col(abcd_data)
      } else {
        abcd_data$n_bu <- 1
      }
      
      while (greedy_sampling_ratio > greedy_lr * 2) {
        current_samples <- list()
        
        for (i in 1:n_sampling_attempts) {
          
          # take a random sample of companies
          sampled_companies <-abcd_data |>
            distinct(company_id, n_bu) |>
            sample_frac(greedy_sampling_ratio, weight=.data$n_bu) 
          
          sampled_data <-
            abcd_data |> filter(company_id %in% sampled_companies$company_id)
          
          # compute the total production of the sample
          sampled_prod_volume_per_group <- sum_total_prod_volume(sampled_data, group_cols=group_cols)
          
          # then compute the volume this total production represents regarding the full data
          new_ratio <-
            inner_join(
              sampled_prod_volume_per_group,
              full_prod_volume_per_group,
              by = group_cols
            ) |>
            mutate(perc_prod_kept = plan_tech_prod.x / plan_tech_prod.y)
          
          # compute the total yearly prod on 
          yearly_sampled_prod_volume_per_group <- sum_yearly_prod_volume(sampled_data, group_cols=group_cols)
          
          # compute the RMSE per group between full and sampled datasets' yearly productions
          rmse <- calculate_rmse(
            yearly_full_prod_volume_per_group,
            yearly_sampled_prod_volume_per_group,
            group_cols=group_cols
          )
          
          # compute the average rmse as the evaluation metric
          avg_rmse <- mean(rmse)
          
          current_samples[[i]] <-
            list(
              data = sampled_data,
              ratio_diff = mean(abs(new_ratio$perc_prod_kept - uniform_ratio)),
              rmse = avg_rmse
            )
        }
        
        # Find the best sample in this iteration according to the rmse
        best_sample_in_iteration <- sapply(current_samples, function(x) x$rmse)
        min_diff_index <- which.min(best_sample_in_iteration)
        
        print(current_samples[[min_diff_index]]$ratio_diff)
        
        # select the sample having best RMSE in the sample, if it is better than last ratio_diff
        if (current_samples[[min_diff_index]]$ratio_diff < best_ratio_diff) {
            
            best_sample <- current_samples[[min_diff_index]]$data
            best_ratio_diff <- current_samples[[min_diff_index]]$ratio_diff
            best_rmse <- current_samples[[min_diff_index]]$rmse
          
        }
        
        greedy_sampling_ratio <- greedy_sampling_ratio - greedy_lr
      }
      return(best_sample |> select(-c(n_bu)))
    }
  

```



# Load or generate ABCD input

```{r}
if (!file.exists(here::here("data-raw", "st_inputs", "abcd_stress_test_input.csv"))) {
  source(file = here::here("data-raw", "run_prepare_abcd_stress_test_input.R"))
} 
abcd_full <- readr::read_csv(here::here("data-raw", "st_inputs", "abcd_stress_test_input.csv"))
```

# Sample the data 

```{r}

# Set the grouping cols to be used as stratas for the sampling
group_cols <- c("scenario_geography", "ald_sector", "ald_business_unit")

abcd_sampled <- sample_companies_greedy(
  abcd_full, 
  group_cols=group_cols,
  uniform_ratio = 0.5,
  use_weighting=FALSE
  )

```

# Revert to original data, and recreate abcd data

## Create sampling filter
```{r}
data(scenarios_geographies) #loaded from package

sample_selection <- abcd_sampled %>%
  distinct(company_id, ald_sector, ald_business_unit, scenario_geography) %>%
  inner_join(
    scenarios_geographies %>% 
      rename(ald_location=country_iso) %>%
      distinct(scenario_geography_newname, ald_location),
    by = c("scenario_geography" = "scenario_geography_newname"),
    relationship = "many-to-many"
  ) %>%
  select(c(company_id, ald_sector, ald_business_unit, ald_location)) %>%
  distinct_all() # distinct all because different geographies can share the same country

```

## recreate abcd with filtering  // duplicate of data-raw/run_prepare_abcd_stress_test_input.R

```{r}
## PARAMETERS

output_path_stress_test_input <-
  here::here(
    "data-raw",
    "st_inputs",
    "sample_abcd_stress_test_input.csv"
)
  

start_year <- 2022 
time_horizon <- 5
additional_year <- NULL
sector_list <- c("Automotive", "Power", "Oil&Gas", "Coal")
km_per_vehicle <- 15000

DB_company_activities  <-   arrow::read_parquet(here::here("data-raw","DBs","DB_company_activities.parquet")) %>%
  inner_join(sample_selection)
DB_company_emissions  <-  arrow::read_parquet(here::here("data-raw","DBs","DB_company_emissions.parquet"))%>%
  inner_join(sample_selection)

abcd_stress_test_input <-
  prepare_abcd_data(
    company_activities = DB_company_activities,
    company_emissions = DB_company_emissions,
    scenarios_geographies = scenarios_geographies, # loaded from package
    start_year = start_year,
    time_horizon = time_horizon,
    additional_year = additional_year,
    km_per_vehicle = km_per_vehicle,
    sector_list = sector_list
  )

abcd_stress_test_input %>% 
  assertr::verify(all(colSums(is.na(.)) == 0))

abcd_stress_test_input %>% readr::write_csv(output_path_stress_test_input)
```



# Evaluate sampling 

```{r}

## Aggregations full

n_companies_full <- count_n_companies(abcd_full, group_cols=group_cols)
company_volume_prod_full <- sum_company_prod_volume(abcd_full, group_cols=group_cols)
total_volume_prod_full <- sum_total_prod_volume(abcd_full, group_cols=group_cols)
yearly_volume_prod_full <- sum_yearly_prod_volume(abcd_full, group_cols=group_cols)


## Aggregations sampled

n_companies_sampled <- count_n_companies(abcd_stress_test_input, group_cols=group_cols)
company_volume_prod_sampled <- sum_company_prod_volume(abcd_stress_test_input, group_cols=group_cols)
total_volume_prod_sampled <- sum_total_prod_volume(abcd_stress_test_input, group_cols=group_cols)
yearly_volume_prod_sampled <- sum_yearly_prod_volume(abcd_stress_test_input, group_cols=group_cols)

```



## Summary dataframes

### Number of companies per sector & BU

```{r message=FALSE, warning=FALSE}
for (scenario in unique(abcd_stress_test_input$scenario_geography)){
  companies_comparison <- inner_join(
    abcd_full|> 
    dplyr::filter(scenario_geography == scenario) |>
    count_n_companies(group_cols=group_cols)
    , 
    abcd_stress_test_input |> 
    dplyr::filter(scenario_geography == scenario)  |>
    count_n_companies(group_cols=group_cols),
    by=c("scenario_geography", "ald_sector", "ald_business_unit"),
    suffix = c(".full", ".sampled")
  )
  


# Pivot the data
data_long <- companies_comparison %>%
  pivot_longer(cols = c("n_companies.full", "n_companies.sampled"),
               names_to = "company_type",
               values_to = "n_companies")

# Create the plot
plot <- ggplot(data_long, aes(x = interaction(ald_sector, ald_business_unit), y = n_companies, fill = company_type)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = unique(data_long$scenario_geography),
       x = "Sector and Business Unit",
       y = "Number of Companies") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(plot)

  }
```



### diff companies, production,  between full and sampled

```{r}
# comp_n_companies <- inner_join(n_companies_full, n_companies_sampled, by=group_cols, suffix=c(".full", ".sampled"))
# 
# comp_total_volume_prod <- inner_join(total_volume_prod_full, total_volume_prod_toydata, by=group_cols, suffix=c(".full", ".sampled")) |> mutate(perc_prod_kept = plan_tech_prod.toydata / plan_tech_prod.fulldata)
# 
# o <- inner_join(comp_n_companies, comp_total_volume_prod, by=group_cols) |>
#   select(ald_sector, ald_business_unit, n_companies.fulldata, n_companies.toydata, perc_prod_kept)
#   
# 
# # inner_join(
# # inner_join(
# #   abcd_full_global|> 
# #   group_by(ald_sector, ald_business_unit, ald_production_unit) |>
# #   summarise(total_prod = sum(plan_tech_prod), .groups="drop") |>
# #   group_by(ald_production_unit) |>
# #   mutate(perc_prod_total_full = as.integer(total_prod/sum(total_prod) * 100)) |>
# #   ungroup() |>
# #   select(-c(total_prod))
# #   , 
# #   abcd_data|> 
# #   group_by(ald_sector, ald_business_unit, ald_production_unit) |>
# #   summarise(total_prod = sum(plan_tech_prod), .groups="drop") |>
# #   group_by(ald_production_unit) |>
# #   mutate(perc_prod_total = as.integer(total_prod/sum(total_prod) * 100)) |>
# #   ungroup() 
# # 
# #   ),
# #   
# #     abcd_data |> 
# #   dplyr::distinct(ald_sector, ald_business_unit, company_id) |> # remove duplicates on year 
# #   dplyr::group_by(ald_sector, ald_business_unit) |>
# #   dplyr::summarise(n_companies=n())
# # )|>
# #   mutate(
# #     prod_company_provided = round(total_prod/n_companies, 3),
# #     prod_company_provided_perc = prod_company_provided/total_prod
# #   )
# 
# 
# ladata <- inner_join(
# abcd_full_global |>
#     group_by(ald_sector, ald_business_unit, ald_production_unit) |>
#     summarise(bu_prod_full = sum(plan_tech_prod), .groups = "drop") |>
#     group_by(ald_production_unit) |>
#     mutate(
#       unit_prod_full = sum(bu_prod_full),
#       perc_bu_prod_full = as.integer(bu_prod_full / unit_prod_full * 100)
#     ) |>
#     ungroup()
#   
#   ,
# inner_join(
#   abcd_data |>
#     dplyr::distinct(ald_sector, ald_business_unit, company_id) |> # remove duplicates on year
#     dplyr::group_by(ald_sector, ald_business_unit) |>
#     dplyr::summarise(n_companies = n())
#   ,
#   abcd_data |>
#     group_by(ald_sector, ald_business_unit, ald_production_unit) |>
#     summarise(bu_prod = sum(plan_tech_prod), .groups = "drop") |>
#     group_by(ald_production_unit) |>
#     mutate(
#       unit_prod = sum(bu_prod),
#       perc_bu_prod = as.integer(bu_prod / unit_prod * 100)
#     ) |>
#     ungroup()
#   
# ) |>
#   mutate(
#     prod_company_in_bu = bu_prod / n_companies,
#     prod_company_in_unit = round(prod_company_in_bu / unit_prod * 100, 3)
#   )
# 
# )|> 
#   select(ald_sector,
#          ald_business_unit,
#          perc_bu_prod,
#          perc_bu_prod_full,
#          prod_company_in_unit) |>
#   inner_join(o) |>
#   mutate(perc_companies_kept = n_companies.toydata / n_companies.fulldata)
# 
# 
# ladata
# ```
# 
# 
# ## Plotting
# 
# ### diff yearly prod full vs toy
# 
# ```{r echo=FALSE, fig.height=6, fig.width=8}
# comp_yearly_volume_prod <-
#   inner_join(
#     yearly_volume_prod_full,
#     yearly_volume_prod_sampled,
#     by = c(
#       "scenario_geography",
#       "year" ,
#       "ald_sector",
#       "ald_business_unit"
#     ),
#     suffix = c(".fulldata", ".sampled")
#   )
# 
# 
# long_data <- comp_yearly_volume_prod |>
#   tidyr::pivot_longer(
#     cols = starts_with("plan_tech_prod"),
#     names_to = "production_type",
#     values_to = "production_value"
#   )
# 
# # Loop through each combination and create a plot
# for (geography in unique(long_data$scenario_geography)) {
#   # Subset the data for the current combination
#   subset_data <- long_data |>
#     filter(
#       scenario_geography == geography
#     )
#   
#   # Create the plot
#   p <-
#     ggplot(
#       subset_data,
#       aes(
#         x = year,
#         y = production_value,
#         color = production_type,
#         group = production_type
#       )
#     ) +
#     geom_line(aes(linetype = production_type)) +
#     facet_wrap( ~ald_sector+ald_business_unit, scales="free_y")+
#     theme_minimal() +
#     labs(
#       title = paste(
#         "Production Comparison:",
#         geography
#       ),
#       x = "Year",
#       y = "Production Value",
#       color = "Production Type"
#     ) +
#     theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#     scale_linetype_manual(values = c("twodash", "dotted"))
#   
#   # Print the plot
#   print(p)
# }
```
